\documentclass[a4paper,12pt,twoside]{scrartcl}
\input{preamble}
\begin{document}
\maketitle
\tableofcontents
\clearpage


%=======================================================================
\section{Introduction}
\label{sec:introduction}
The \abbr{MIA} project is based around monitoring.
Everything starts with setting up the necessary monitoring and then implementing the required changes to make the monitoring check succeed.
It's comparable to test-driven programming where you first write the check and then the function to satisfy the check.
This way the monitoring is never an afterthought and you know from the get-go that the monitoring works.


%=======================================================================
\section{Scope of the project}
\label{sec:scope}
The main focus of the project will be web and mail hosting, including \abbr{DNS}.
We will assume a greenfield deployment in each of these three scenarios though this will be challenging for the setup of \abbr{DNS}.

%-----------------------------------------------------------------------
\subsection{In scope}

\paragraph{Mail services}
Mail services will include setting up of all necessary \abbr{DNS} records, a Postfix email server for a single domain, an \abbr{IMAP} server for mail retrieval and possibly a webmail client though this will require setting up a website, load balancer\ldots

\paragraph{Web services}
Setting up a website will include the application server, database, web server, load balancer, certificates, and \abbr{DNS} records.

\paragraph{Single sign-on}
Authenticating against the different services and especially for accessing your emails should be possible using your Microsoft Active Directory account.

\paragraph{Remote access \abbr{VPN}}
This topic might become in-scope if I can find a way to make it work easily.
The problem will be configuring the local firewall to allow for inbound traffic.

\paragraph{Virtualization}
There will be a choice between spinning up new virtual machines, creating containers, or jails (FreeBSD).
In case a new virtual machine (cloud \abbr{VPS}) is created for each server, costs may increase significantly but the general performance might be better.
Linux containers and FreeBSD jails will require an initial set of cloud \abbr{VPS} instances to run the containers or jails on.

%-----------------------------------------------------------------------
\subsection{Out of scope}
The local network will out of scope, i.e., this project does not aim to monitor and configure local switches or firewalls.


%=======================================================================
\section{Initialization}
\label{sec:initialization}
During the initial setup the decision will have to be made for virtual machines or jails.
Either way at least two new virtual machines will have to be created with Digital Ocean or AWS.
Perhaps a manual option should be provided so that you can enter the \abbr{IP} addresses or domain names and the root credentials of two VMware vSphere virtual machines hosted locally.

Next you need to enter your domain name.
If you want to import the existing (public) zone configuration, you will either have to upload the zone file or allow the \abbr{MIA} box to do an \abbr{AXFR} zone transfer from the existing \abbr{DNS} servers.
Either way, manual actions will be needed to setup your two new name servers as the authoritative name servers for the domain.
Example configurations should be provided for a few major hosting companies, e.g., GoDaddy.
Even better would be if they provide an \abbr{API} so \abbr{MIA} can do these actions automatically.


%=======================================================================
\section{Single sign on}
\label{sec:sso}
The first two servers have been setup to host the (public) domain name.
Now we should get \abbr{SSO} to work so you can easily connect to these and future servers and services.

To enable this a new virtual machine or jail will be set up with \abbr{389DS} running on it which will do a one-way sync from the on-premise Active Directory to \abbr{389DS}.


%=======================================================================
\section{Services}
\label{sec:services}

%-----------------------------------------------------------------------
\subsection{Email services}
Setting up an email server requires two new virtual machines running the Postfix \abbr{SMTP} server and two more virtual machines running the Dovecot \abbr{IMAP} server.
Additionally several \abbr{DNS} records need to be added.
These include \abbr{MX} and \abbr{SPF} but also \abbr{SSHFP} records for the new virtual machines.

Enabling webmail will create a lot of complexity as Roundcube requires a web server, \abbr{PHP}, and a database.
Our philosophy of allowing dynamic growth and redundancy will add load balancer to this traffic flow.

%-----------------------------------------------------------------------
\subsection{Web services}
The addition of a single static website requires a minimum of four new virtual machines.
In addition to two new web servers two load balancers will have to be created---unless they already exist in which case their configuration will have to be updated.
The content of the website will be fetched using a \texttt{git clone} and \texttt{git checkout}.

Dynamic websites require the addition of application and database servers.
Database servers can be shared between different services.
It has to be investigated whether or not the application servers can be used for several different websites but this is most likely the case as well.

%-----------------------------------------------------------------------
\subsection{Databases}
The database server is an ``internal'' server.
It will only host databases required by the services offered by \abbr{MIA}.
It will thus only host databases automatically created by software such as Roundcube or WordPress.
There is no need for a user to manually access the database server.

%-----------------------------------------------------------------------
\subsection{Load balancing}
The two load balancers form an active/standby cluster and direct the incoming sessions to the different web servers.

%-----------------------------------------------------------------------
\subsection{Application servers}
Application servers for the websites can be either \abbr{PHP} or Python application servers.


%=======================================================================
\section{Monitoring}
\label{sec:monitoring}




\end{document}